A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2023-02-10 papers/paper1/ms.tex
Added citation for Cao

\authorcomment1{General background information and motivation for starspots...}

@@

\authorcomment1{Todo: Cite Lyra Cao et al. in prep-- estimated August 2022}.

>>>>

Imperfections on the Sun's surface have been observed with telescopes for over 400 years \citep{1613idim.book.....G}.  The mere existence of these sunspots betrayed an inexact understanding of the Sun, departing from the Platonic solid yellow circular disk that still prevails in cartoon pictures today.  The existence of starspots on other stars was realized 75 years ago \citep{1947PASP...59..261K}, and has since enabled the entirely new subfields of gyrochronology, Doppler imaging, and stellar activity.  Our community now takes for granted the omnipresence of starspots to measure rotation periods for 34,030 stars in the \emph{Kepler} mission \citep{2014ApJS..211...24M}, and about 29,860 stars in the \emph{K2} mission \citep{2020A&A...635A..43R}.  The \emph{TESS} mission continues to collect lightcurves for millions of stars, making it destined to measure periods for hundreds of thousands of stars \citep{2022ApJ...927..219C}.

@@

In \citet{2022arXiv220910549C}, they borrow an equation from \citet{somers151}. In this equation, they define the variable $x_\mathrm{spot}$ as the ratio of $T_\mathrm{spot}$ over $T_\mathrm{ambient}$.
